Linear response theory for core set identification

### 2012-05-21 writedown/linear.response/langevin.tex
small revise
fix bugs in text

q, \vect p\}$) is subject to the Fokker-Planck equation:

@@

where $\fwg$ is the infiniesimal generator gieven by

@@

distribution (invariant measure) and the unperturbed operator,

@@

The Fokker-Planck equation for the perturbation is therefore

@@

term $\Delta\fwg(t)  \Delta  f(\vect x, t)$ in the Fokker-Planck equation

@@

Fokker-Planck

@@

The operator on l.h.s. is the same as the unperturbed Fokker-Planck equation.

@@

it has been shown that~\cite{tuckeman2010statistical}

@@

  f_0(\vect x) j(\vect x)  \\

@@

Where $\bwg_0$ is the infiniesimal generator of the \emph{unperturbed} backward
Kolmogorov equation, which is the adjoint operator of $\fwg_0$.

@@

\subsection{The Core set as an observation of the system}

>>>>

q, \vect p\}$) is subject to the Kolmogorov forward equation:

@@

where $\fwg$ is the forward infiniesimal generator gieven by

@@

distribution (invariant measure) and the unperturbed operator
($\vect C = \vect D = 0$),

@@

The Kolmogorov forward equation for the perturbation is therefore

@@

term $\Delta\fwg(t)  \Delta  f(\vect x, t)$ 

@@

Kolmogorov forward equation

@@

The operator on l.h.s. is the same as the unperturbed equation.

@@

it has been shown that %~\cite{tuckeman2010statistical}

@@

  f_0(\vect x) j(\vect x)  \\\nonumber

@@

Where $\bwg_0$ is the infiniesimal generator of the \emph{unperturbed} 
Kolmogorov backward equation, which is the adjoint operator of $\fwg_0$.

@@

\subsection{The core set as an observation of the system}
